Xolotl: An Intuitive and Comprehensible Neuronal Simulator

### 2018-05-23 PaperLatex/frontiers.tex
Add to Simulation section

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}
\usepackage{natbib}
\usepackage{placeins}
\usepackage{matlab-prettifier}
\linenumbers

@@

This model was constructed using conductances from Liu \textit{et al} 1998. In the absence of applied positive current, the model is quiescent and tonically spikes under 0.2 nA of applied current (\ref{fig:figurehh}D). The \texttt{integrate} function takes the applied current as an argument (e.g. \texttt{x.integrate(AppliedCurrent)}), so that the \texttt{xolotl} object is agnostic to integration-specific perturbations. The \texttt{plot} function generates voltage and intracellular calcium traces, where the voltage trace is colored by the dominant current. If the membrane potential is increasing, the strongest instantaneous inward current colors the trace. Conversely, if the membrane potential is decreasing, the strongest outward current colors the trace instead. \ref{fig:figurehh}F-I display the results of the \texttt{show} function. Activation and inactivation steady-states and the voltage-dependent time constants of these gating variables describe the conductance dynamics in absence of other channel types.

@@

\texttt{cpplab} comes with several features which simplify the handling of high-dimensional models. The \texttt{find} function acquires a cell array of all properties of the network which satisfy a search condition.

@@

Simulations can be run in "open-loop" mode where each simulation begins by resetting all dynamical variables to their initial conditions at instantiation, or "closed-loop" mode which begins simulation with the current network state.

@@

\texttt{xolotl} comes packaged with a graphical user interface for visualizing parameter changes in real-time. The \texttt{manipulate} function begins the

@@

\section*{Supplemental Data}
 Table including all conductances packaged with \texttt{xolotl} should be put in the supplementary material.

>>>>

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}
\usepackage{natbib}
\usepackage{placeins}

\usepackage{xcolor}
\usepackage{listings}
\usepackage{matlab-prettifier}
\lstMakeShortInline[style=Matlab-editor]"

\linenumbers

@@

This model was constructed using conductances from Liu \textit{et al} 1998. In the absence of applied positive current, the model is quiescent and tonically spikes under 0.2 nA of applied current (\ref{fig:figurehh}D). The \texttt{integrate} function takes the applied current as an argument (e.g. "x.integrate(AppliedCurrent)"), so that the \texttt{xolotl} object is agnostic to integration-specific perturbations. The \texttt{plot} function generates voltage and intracellular calcium traces, where the voltage trace is colored by the dominant current. If the membrane potential is increasing, the strongest instantaneous inward current colors the trace. Conversely, if the membrane potential is decreasing, the strongest outward current colors the trace instead. \ref{fig:figurehh}F-I display the results of the \texttt{show} function. Activation and inactivation steady-states and the voltage-dependent time constants of these gating variables describe the conductance dynamics in absence of other channel types.

@@

\texttt{cpplab} comes with several features which simplify the handling of high-dimensional models. The \texttt{find} function acquires a cell array of all properties of the network which satisfy a search condition. For example, one can find all paths to maximal conductances within the "'HH'" compartment in two ways:

\begin{lstlisting}[style=Matlab-editor]
	x.find('HH*gbar');
	x.HH.find('gbar');
\end{lstlisting}

To extract a vector of the maximal conductances:

\begin{lstlisting}[style=Matlab-editor]
	gbars = x.get(x.find('HH*gbar'));
\end{lstlisting}

To set the maximal conductances all at once:

\begin{lstlisting}[style=Matlab-editor]
	x.set(x.find('HH*gbar'), gbars)
\end{lstlisting}

"MATLAB" can easily control the "cpplab" objects using the standard, flexible data structure notation popular in high-level scripting languages.

@@

Simulations can be run in 'open-loop' mode where each simulation begins by resetting all dynamical variables to their initial conditions at instantiation, or 'closed-loop' mode which begins simulation with the current network state.

@@

\texttt{xolotl} comes packaged with a graphical user interface for visualizing parameter changes in real-time. The \texttt{manipulate} function opens the GUI, which displays a figure plotting the membrane potential and intracellular calcium concentration of all compartments as time series, and a dialog box with customizable sliders for all parameters of the model. Moving the sliders integrates the model in `open-loop` mode with the new parameters. The parameters available in the sliders can be customized by passing a cell array to manipulate. For example, to only see sliders for maximal conductances of the "HH" compartment, call "x.manipulate(x.find('HH*gbar'))". Closing the GUI saves the network state of the model to the "xolotl" object. This is particularly helpful for rapid prototyping of models.

@@

\section*{Supplemental Data}
 Tables including all conductances packaged with \texttt{xolotl} should be put in the supplementary material.
